|

### 2020-11-22 nontex/install/git/fs_git_setup.Rmd
additional installation guides

```{bash}
git tag -l
git tag -a v0.1.1 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
git show v0.1.1
git push github v0.1.1
```

## Githug pages

@@

>>>>

```{bash}
git tag -l
git tag -a v0.1.3 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
git tag -a v0.1.37 -m "pyfan with sphinx"
git show v0.1.37
git push github v0.1.37
```

## Github pages

@@

# Git Commands

## Stop tracking a particular file

```
cd ~/PrjOptiSNW
git filter-branch --tree-filter 'rm -f ~/PrjOptiSNW/PrjOptiSNW.mltbx' -- --all
```

### 2020-11-22 nontex/install/windows/fn_installations.Rmd
additional installation guides

---
title: |
  | New Computer Fan Data-Science Set-up
  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
  | Atom, VScode, Pycharm
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

@@

```{bash}
# poetry
curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
# sphinx
pip install sphinx
```

Theme for sphinx
```{bash}
pip install sphinx-rtd-theme
pip install sphinx_bootstrap_theme
```

@@

@@

```{bash}
poetry remove python-frontmatter pyyaml
poetry add python-frontmatter pyyaml
```

@@

```{bash}
cd ~/pyfan
cd "C:/Users/fan/pyfan"
poetry install

rm -rf dist/ build/ docs/
cd docs/
sphinx-build -b html ../ _build
<!-- make html -->
sphinx-build -b latexpdf ../ _build
make latexpdf

@@

On some local computer install pyfan:

@@

##### pyfan workflow and files added

@@

```{bash}
cd "C:/Users/fan/pyfan"
poetry install

rm -rf dist/ build/ docs/
mkdir docs
cd docs/
sphinx-build -b html ../ _build

```{bash}
pip show pyfan
<!-- pip install pyfan -->
pip uninstall pyfan -y
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan

conda activate wk_pyfan
pip uninstall pyfan -y
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
conda deactivate
```

@@

@@

@@

```{bash}
# if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all
```

@@

# see if package exists on pip and install from pip
pip install smop
```

@@

#### Conda revealjs nodejs Environment

@@

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_pyfan
conda create -n wk_pyfan -y
conda activate wk_pyfan

# add channel
conda config --env --add channels conda-forge
conda config --get channels
conda config --get channels --env

# yaml
conda install python-frontmatter -y
conda install pyyaml -y

# environment data
conda install cdsapi -y
conda install -c conda-forge eccodes -y

@@

@@

@@

@@

# Inside Conda base
conda activate
# Conda r_env
conda activate r_env
# Where is it installed?
which R
# /home/wangfanbsg75/anaconda3/bin/R
conda uninstall r-base
```

@@

@@

- [reticulate](https://github.com/rstudio/reticulate)

@@

# Install tidyverse
install.packages(c("tidyverse", "tidymodels"))

@@

# Install Tools to Work with Other Packages
install.packages(c("reticulate", "JuliaCall"))

# Personal Packages
devtools::install_github("fanwangecon/REconTools")
```
```{r}
# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
# Install R-tools, RTOOLS is for WINDOWS
# install.packages("installr")
# library("installr")
# install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

@@

@@

@@

@@

### Atom Shortcuts and Features

@@

- Git Pane: *Ctrl + 9*, *Ctrl + 8*

@@

### Sublime and Outline (Markdown)

@@

@@

@@

- Auto-Indent: *CTRL + SHIFT + ALT + L*

## Other Editors

### Notepad++

@@

>>>>

---
title: |
  | Data-Science Set-up
  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
  | VScode, Atom, Sublime Pycharm
output:
  html_document:
    number_sections: true
    toc: yes
  html_notebook:
    number_sections: true
    toc: yes
  word_document:
    number_sections: true
  pdf_document:
    df_print: paged
    number_sections: true
    toc: yes
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/). This file contains various excessive details on installations.

@@

```{bash}
# poetry
curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
poetry --version
# sphinx
pip install sphinx
```

Theme for sphinx
```{bash}
pip install sphinx-rtd-theme
pip install sphinx_bootstrap_theme
pip install nbsphinx --user
```

@@

### Poetry Update Python Version

[poetry change python version to 3.x](https://stackoverflow.com/questions/60580113/poetry-change-python-version-to-3-x)

The existing poetry env needs to be deleted and re-created if need to update python version.

```{bash}
poetry env list 
```

1. Update python requirement in .toml to *python = "^3.8"*
2. delete current env: *poetry env remove python*
3. run: *poetry lock*
4. run: *poetry update*, *poetry install*, etc...

@@

```{bash}
# pyfan
poetry remove python-frontmatter pyyaml
poetry add python-frontmatter pyyaml
poetry add numpy
poetry add scipy
poetry add cython

# Compuational and Stats
poetry add statsmodels
poetry add numba
poetry add sklearn

# visualize
poetry add matplotlib
poetry add seaborn

# pyecon
poetry add pyfan

# aws
poetry add boto3
```

@@

SEE BELOW *pyfan/pyecon workflow and files added*:

```{bash}
cd ~/pyfan
cd "C:/Users/fan/pyfan"
cd "C:/Users/fan/pyecon"
poetry install

<!-- rm -rf dist/ build/ docs/
mkdir docs -->
cd doc/
rm -rf _build/ auto_examples/ gen_modules/backreferences gen_modules/generators
sphinx-build -b html ../ _build
<!-- make html -->
sphinx-build -b latexpdf ../ _build
make latexpdf

@@

SEE BELOW *pyfan/pyecon workflow and files added*, on some local computer install pyfan:

@@

##### pyfan/pyecon workflow and files added

@@

```{bash}
conda activate base

<!-- to update all dependencies -->
poetry update

cd "C:/Users/fan/pyfan/"
cd "C:/Users/fan/pyecon/"
poetry install

cd "C:/Users/fan/pyfan/doc/"
cd "C:/Users/fan/pyecon/doc"
rm -rf _build/ auto_examples/ gen_modules/backreferences gen_modules/generators
make html

<!-- Check Results in: C:\Users\fan\pyfan\doc\_build\html\index.html -->

cd "C:/Users/fan/pyfan/"
cd "C:/Users/fan/pyecon/"
poetry build
poetry publish
```

pip install works inside conda env. Uninstall first. Then install pyfan in conda env using pip. With user option, seems to install system-wide.

Note that if some of the conda env use different python versions than base, then when base programs are updated, will not update in env.

Might need to update this in all sub-directories

```{bash}
<!-- local install, this does not install in conda env -->
cd "C:/Users/fan/pyfan/"
cd "C:/Users/fan/pyecon/"
python setup.py install --user
<!-- after installing show appear under pip: pip show pyfan, with latest version ID -->
<!-- after installing this does not appear on conda list: conda list -n base, but in python, import pyfan as pyfan works -->
<!-- help('modules') in python to see if installed-->

pip show pyfan
<!-- pip install pyfan -->
pip uninstall pyfan -y
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan

conda activate wk_pyfan
conda activate wk_cgefi

<!-- if pyfan already installed, but not in conda env, uninstall and installing puts it in conda env -->
pip uninstall pyfan -y
pip install pyfan
<!-- --user installs it for outside of env -->
pip install pyfan --user

pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
conda deactivate
```

@@

2. install sphinx packages

- [phinx-gallery](https://sphinx-gallery.github.io/stable/index.html)

```{bash}
pip install sphinx-gallery
```

@@

Conda update python version

```{bash}
conda install -c anaconda python=3.7
conda update --all
```

@@

```{bash}
# if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
# to show all currently installed: conda list -n base
conda update --all
```

@@

# see if package exists on pip and install from pip
pip install smop
```
#### Conda Base

```{base}
conda install -c anaconda boto3 -y

@@

#### Conda wk_pyfan bookdown

@@

```{r}
conda update -n base -c defaults conda

# Set up
conda deactivate
conda list env
conda env remove -n wk_pyfan
conda create -n wk_pyfan -y python=3.8
conda activate wk_pyfan

# add channel
# conda config --env --add channels conda-forge
conda config --get channels
conda config --get channels --env

# yaml
# conda install python-frontmatter -y
pip install python-frontmatter
conda install pyyaml -y

@@

# numpy etc install
conda install -c anaconda numpy
# https://github.com/numpy/numpy/issues/17726
# https://github.com/numpy/numpy/wiki/FMod-Bug-on-Windows
# pip install numpy==1.19.3
# conda install -c anaconda cython

# matplotlib install
# conda install -c anaconda matplotlib -y
# python -m pip install -U matplotlib

# to test aws
conda install boto3 -y

# environment data
conda install cdsapi -y
conda install -c conda-forge eccodes -y
conda install -c conda-forge cfgrib

@@

#### Conda ECMWF Envir

conda deactivate
conda list env
conda env remove -n wk_ecmwf
conda create -n wk_ecmwf -y
conda activate wk_ecmwf

conda install -c conda-forge cdsapi -y
conda install -c conda-forge eccodes -y
conda install -c conda-forge cfgrib -y
conda install -c conda-forge xarray -y
conda install -c conda-forge netcdf4 -y

#### Conda ECMWF Envir Python 2

conda deactivate
conda list env
conda env remove -n wk_ecmwf_py2
conda create -n wk_ecmwf_py2 python=2.7 -y 
conda activate wk_ecmwf_py2

python --version
```

#### Conda CGE Environment

Installing pip installed/updated python version from 3.7 to 3.8.

```
conda deactivate
conda list env
conda env remove -n wk_cgefi
conda create -n wk_cgefi -y
conda activate wk_cgefi

# Install External Tools
conda install -c anaconda pip -y

# Cloud
conda install -c anaconda boto3 -y

# Python tools
conda install -c anaconda pytest -y

# Install Own Tools
pip install pyfan

# Scientific Computing
conda install -c anaconda numpy -y
conda install -c anaconda statsmodels -y
conda install -c conda-forge interpolation -y
conda install -c anaconda pandas -y
conda install -c anaconda scikit-learn
conda install -c anaconda cython

# Graphing
conda install -c anaconda matplotlib -y
conda install -c anaconda pillow -y

#### Conda AWS Environment

AWS environment and set-up on local computer

```
conda deactivate
conda list env
conda env remove -n wk_aws
conda create -n wk_aws -y
conda activate wk_aws

install docker
```

@@

## Numpydoc

```{bash}
Returns:
    None

@@

# Inside Conda base
conda activate
# Conda r_env
conda activate r_envr
# Where is it installed?
which R
# /home/wangfanbsg75/anaconda3/bin/R
conda uninstall r-base
```

@@

### Update R

1. On windows, install the *installr* package, and use *updateR()*
2. At the end, will ask if want to move all old pacages to new R directory

New R will have new package directory, could keep all in old, should copy all to new, and not keep old.

```{r}
# https://www.r-project.org/nosvn/pandoc/installr.html
install.packages('installr')
# update R from inside R (not Rstudio)
require(installr)
# this will open dialog boxes to take you through the steps.
updateR() 
# Set Rstudio to the Latest R
```

@@

- [reticulate](https://github.com/rstudio/reticulate)
    + install directly from: devtools::install_github("rstudio/reticulate")

@@

# Install system tools
install.packages(c("backports"))

# Install tidyverse
install.packages(c("tidyverse", "tidymodels", "vroom"))

@@

# Install Tools to Work with Other Packages
install.packages(c("reticulate", "JuliaCall"))
# for reticulate errors, install directly from: devtools::install_github("rstudio/reticulate")

# Paralell
install.packages(c("parallel", "doParallel", "foreach"))

# Personal Packages
devtools::install_github("fanwangecon/REconTools")
devtools::install_github("fanwangecon/PrjOptiAlloc")
```
```{r}
# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
# Install R-tools, RTOOLS is for WINDOWS
# install.packages("installr")
# library("installr")
# install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

@@

# Matlab Installation

1. go to Mathworks, download the latest file.s

# Word

[Change background color and text color in word](https://www.davidbosman.fr/scsaw/?p=687)

Use these for my preferred background and text colors, consistent with SumatraPDF

> TextColor = #1e170f, R=30, G=23, B=15
> BackgroundColor = #fff8e6, R=255, G=248, B=230

@@

Editors to Install:

1. Notepad++: for sync with Sumatra and quick edit by section, and fast quick editor in general
2.

@@

### VSCode and Python

#### Virtual Env Python VSCode

(Using Python environments in VS Code)[https://code.visualstudio.com/docs/python/environments]

1. Ctrl + Shift + P
2. type in: Python: Select Interpreter

@@

### Atom Shortcuts, Features and Settings

@@

- Git Pane: *Ctrl + 9*, *Ctrl + 8*
- Hard Wrap Text: *Ctrl + Shift + q*

**Spellcheck Scope** :

- cmd+shift+p, run *Editor: Log Cursor Scope*, see notification that comes up, add the *scopes* found to the *spell-check* package scope list.

@@

### Sublime Shortcut

- *json pretty*, "alt + shift + j"
### Sublime and Outline (Markdown)

@@

## RStudio

### RStudio Short Cuts

**GUI**

- clear all console outputs, collapse all: *edit + clear all outputs*

@@

### PyCharm Settings GUI View etc

Change Theme, modify by changing plug-in.

Go to Settings, *Ctrl + Alt + S*, inside settings, go to theme/appearances, and chagne which theme is used. Material theme has a number of different options.

- Change where Tabs are displayed top or side: Settings -> Editor -> Editor Tabs -> Tab Placement (right)
- To change font: Settings -> Color Scheme -> Color Scheme Font ->

### PyCharm Set Virtual Env

1. In conda env: `where python`: `C:\ProgramData\Anaconda3\envs\wk_cgefi\python.exe`
2. In Pycharm: Settings (ctrl+alt+s), Project, Python interpreter.
3. Click on the cog button, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts

@@

**copy/paste**

- copy current function/line reference: *Ctrl + Shift + Alt + C*
- copy current file full path: *Ctrl + Shift + C*

**run/debug/test**

- Run current file: *ctrl+shift+f10*
- Run all tests in current file: *alt+shift+f10*
- Clear all Break-Points: *Ctrl+Shift+F8, Delete*
- Open up evaluator during debug: *Alt + F8*
- right click on a file and choose to run all "pytest", then should start test x of N

**Coding**

[code editor help](https://www.jetbrains.com/help/pycharm/using-code-editor.html)

- Refractor Names: *SHIFT + F6*
- Auto-Indent: *CTRL + SHIFT + ALT + L*
- Upper Case All: "CTRL + SHFT + U"
- Lower Case All: "CTRL + SHFT + L"
- reformat auto-indent: "Ctrl + Alt + L"
- Highlight searched: "Ctrl + Shift + F7"

**GUI**

Switching between panes:

1. set up default: Windows - Store Current as Default, go to default with *Shift + F12*
2. back to editor main: *CTRL + SHIFT + F12*

- Hide All non-code Windows: *CTRL + SHIFT + F12*
- Shift to last active: *F12*
- Maximize Output/Console Pane: *CTRL + SHIFT + QUOTE*
- Hide Output Pane: *SHIFT + ESC*
- Show Console output max: first debug, where debug is activate, *Ctrl + Shift + '*

- Go to Settings: *Ctrl + Alt + S*, click on keymap

## Notepad++

@@

### Installation

- Install Notepad++
- Settings + Preferences + Cloud + Google Drive/App/Notepad++ Sync Setting there. 
- install [Npp-1-Dark](https://github.com/60ss/Npp-1-Dark)
